
References
----------

.. [Kri10] M. R. B. Kristensen and B. Vinter, *Numerical Python for Scalable Architectures*,
            in Fourth Conference on Partitioned Global Address Space Programming Model, PGAS{’}10. ACM, 2010. [Online]. Available: http://distnumpy.googlecode.com/files/kristensen10.pdf

.. [Dav04] T. David, P. Sidd, and O. Jose, *Accelerator : Using Data Parallelism to Program GPUs for General-Purpose Uses*,
            October. [Online]. Available: http://research.microsoft.com/apps/pubs/default.aspx?id=70250

.. [New11] C. J. Newburn, B. So, Z. Liu, M. Mccool, A. Ghuloum, S. D. Toit, Z. G. Wang, Z. H. Du, Y. Chen, G. Wu, P. Guo, Z. Liu, and D. Zhang, *Intels Array Building Blocks : A Retargetable , Dynamic Compiler and Embedded Language*,
             Symposium A Quarterly Journal In Modern Foreign Literatures, pp. 1–12, 2011. [Online]. Available: http://software.intel.com/en-us/blogs/wordpress/wp-content/uploads/2011/03/ArBB-CGO2011-distr.pdf

.. [Klo09] A. Kloeckner, N. Pinto, Y. Lee, B. Catanzaro, P. Ivanov, o and A. Fasih, *PyCUDA and PyOpenCL: A Scripting-Based Approach to GPU Run-Time Code Generation*,
            Brain, vol. 911, no. 4, pp. 1–24, 2009. [Online]. Available: http://arxiv.org/abs/0911.3456

.. [Khr10] K. Opencl, W. Group, and A. Munshi, *OpenCL Specification*,
            ReVision, pp. 1–377, 2010. [Online]. Available: http://scholar.google.com/scholar?hl=en\&btnG=Search\&q=intitle:OpenCL+Specification\#2

.. [Nvi10] N. Nvidia, *NVIDIA CUDA Programming Guide 2.0*,
            pp. 1–111, 2010. [Online]. Available: http://developer.download.nvidia.com/compute/cuda/3\2\ prod/toolkit/docs/CUDA\ C\ Programming\ Guide.pdf

.. [Ros10] G. V. Rossum and F. L. Drake, *Python Tutorial*,
            History, vol. 42, no. 4, pp. 1–122, 2010. [Online]. Available: http://docs.python.org/tutorial/

.. [Int08] Intel, *Intel Math Kernel Library (MKL)*,
            pp. 2–4, 2008. [Online]. Available: http://software.intel.com/en-us/articles/intel-mkl/

.. [Mat10] MATLAB, version 7.10.0 (R2010a).
            Natick, Massachusetts: The MathWorks Inc., 2010.

.. [Rrr11] R Development Core Team, *R: A Language and Environment for Statistical Computing, R Foundation for Statistical Computing*,
            Vienna, Austria, 2011. [Online]. Available: http://www.r-project.org

.. [Idl00] B. A. Stern, *Interactive Data Language*,
            ASCE, 2000.

.. [Oct97] J. W. Eaton, *GNU Octave*,
            History, vol. 103, no. February, pp. 1–356, 1997. [Online]. Available: http://www.octave.org

.. [Oli07] T. E. Oliphant, *Python for Scientific Computing*,
            Computing in Science Engineering, vol. 9, no. 3, pp. 10–20, 2007. [Online]. Available: http://ieeexplore.ieee.org/lpdocs/epic03/wrapper.htm?arnumber=4160250

.. [Gar10] R. Garg and J. N. Amaral, *Compiling Python to a hybrid execution environment*,
            Computing, pp. 19–30, 2010. [Online]. Available: http://portal.acm.org/citation.cfm?id=1735688.1735695

.. [Pas05] R. V. D. Pas, *An Introduction Into OpenMP*,
            ACM SIGARCH Computer Architecture News, vol. 34, no. 5, pp. 1–82, 2005. [Online]. Available: http://portal.acm.org/citation.cfm?id=1168898

.. [Cat09] B. Catanzaro, S. Kamil, Y. Lee, K. Asanovi ́ , J. Demmel, c K. Keutzer, J. Shalf, K. Yelick, and O. Fox, *SEJITS: Getting Productivity and Performance With Selective Embedded JIT Specialization*,
            in Proc of 1st Workshop Programmable Models for Emerging Architecture PMEA, no. UCB/EECS-2010-23, EECS Department, University of California, Berkeley. Citeseer, 2009. [Online]. Available: http://www.eecs.berkeley.edu/Pubs/TechRpts/2010/EECS-2010-23.html

.. [And08] R. Andersen and B. Vinter, *The Scientific Byte Code Virtual Machine*,
            in Proceedings of the 2008 International Conference on Grid Computing & Applications, GCA2008 : Las Vegas, Nevada, USA, July 14-17, 2008. CSREA Press., 2008, pp. 175–181. [Online]. Available: http://dk.migrid.org/public/doc/published\ papers/sbc.pdf

.. [Apl00] “why apl?”
            [Online]. Available: http://www.sigapl.org/whyapl.htm

.. [Sci02] R. Pozo and B. Miller, *SciMark 2.0*,
            2002. [Online]. Available: http://math.nist.gov/scimark2/

.. [Bur10] J. Burkardt, *Shallow Water Equations*,
            2010. [Online]. Available: http://people.sc.fsu.edu/∼jburkardt/m\ src/shallow\ water\ 2d/

.. [Bac78] J. Backus, *Can Programming be Liberated from the von Neumann Style?: A Functional Style and its Algebra of Programs*,
            Communications of the ACM, vol. 16, no. 8, pp. 613–641, 1978.

.. [Kri11] M. Kristensen, H. Happe, and B. Vinter, *Hybrid Parallel Programming for Blue Gene/P*,
            Scalable Computing: Practice and Experience, vol. 12, no. 2, pp. 265–274, 2011.

